\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-01-17 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
removed FLAGS_NO_CHECK from the manual

\begin{description}
\item [{\texttt{F90}}] Path to the Fortran90 compiler.
\item [{\texttt{MPIF90}}] Path to MPI Fortran90.
\item [{\texttt{MPI\_FLAGS}}] Some systems require this flag to link to
MPI libraries.
\item [{\texttt{FLAGS\_CHECK}}] Compiler flag for non-critical subroutines.
\item [{\texttt{FLAGS\_NO\_CHECK}}] Compiler flag for creating fast, production-run
code for critical subroutines.
\end{description}
The configuration script automatically creates for each executable a corresponding
\texttt{Makefile} in the \texttt{src/} subdirectoy.
The \texttt{Makefile} contains a number of suggested entries for various
compilers, e.g., Portland, Intel, Absoft, NAG, and Lahey. The software
has run on a wide variety of compute platforms, e.g., various PC clusters
and machines from Sun, SGI, IBM, Compaq, and NEC. Select the compiler
you wish to use on your system and choose the related optimization
flags. Note that the default flags in the \texttt{Makefile} are undoubtedly
not optimal for your system, so we encourage you to experiment with
these flags and to solicit advice from your systems administrator.
Selecting the right compiler and optimization flags can make a tremendous
difference in terms of performance. We welcome feedback on your experience
with various compilers and flags.

@@

\noindent
Edit file \texttt{flags.guess} and put this for \texttt{FLAGS\_CHECK} and \texttt{FLAGS\_NO\_CHECK}:\\

@@

\noindent
\texttt{   FLAGS\_NO\_CHECK="-O3 -qsave -qstrict -qtune=auto -qarch=450d -qcache=auto \\}
\texttt{   -qfree=f90 -qsuffix=f=f90 -g -qlanglvl=95pure -qhalt=w -Q -Q+rank,swap\_all -Wl,-relax"}

>>>>

\begin{description}
\item [{\texttt{F90}}] Path to the Fortran90 compiler.
\item [{\texttt{MPIF90}}] Path to MPI Fortran90.
\item [{\texttt{MPI\_FLAGS}}] Some systems require this flag to link to
MPI libraries.
\item [{\texttt{FLAGS\_CHECK}}] Compiler flags.
\end{description}
The configuration script automatically creates for each executable a corresponding
\texttt{Makefile} in the \texttt{src/} subdirectoy.
The \texttt{Makefile} contains a number of suggested entries for various
compilers, e.g., Portland, Intel, Absoft, NAG, and Lahey. The software
has run on a wide variety of compute platforms, e.g., various PC clusters
and machines from Sun, SGI, IBM, Compaq, and NEC. Select the compiler
you wish to use on your system and choose the related optimization
flags. Note that the default flags in the \texttt{Makefile} are undoubtedly
not optimal for your system, so we encourage you to experiment with
these flags and to solicit advice from your systems administrator.
Selecting the right compiler and optimization flags can make a tremendous
difference in terms of performance. We welcome feedback on your experience
with various compilers and flags.

@@

\noindent
Edit file \texttt{flags.guess} and put this for \texttt{FLAGS\_CHECK}:\\

@@

\noindent
\texttt{   FLAGS\_CHECK="-O3 -qsave -qstrict -qtune=auto -qarch=450d -qcache=auto \\}
\texttt{   -qfree=f90 -qsuffix=f=f90 -g -qlanglvl=95pure -qhalt=w -Q -Q+rank,swap\_all -Wl,-relax"}
